Data Preparation

### 2019-01-10 Data Preparation.Rmd

### Courses
Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. The tibble `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains; `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers; `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. We use a `full_join` to add these variables to the tibble `d_course`.
```{r}
d_ILO_detail <- d_ILO %>% 
  select(Code, ILO) %>%
  unique %>%
  count(Code) %>%
  rename(n_ILO = n)
print(d_ILO_detail)

d_assessment_detail <- d_assessment %>%
  group_by(Code) %>%
  summarise(n_assessment = n(),
            `Assessments Covered` = paste(Assessment, collapse = ", "))
print(d_assessment_detail)

d_AoD_detail <- d_AoD %>%
  group_by(Code) %>%
  summarise(n_AoD = n(),
            `AoD Covered` = paste(AoD, collapse = ", "))
print(d_AoD_detail)
```

```{r}
d_course <- d_course %>%
  full_join(d_ILO_detail       , by = "Code") %>%
  full_join(d_assessment_detail, by = "Code") %>%
  full_join(d_AoD_detail       , by = "Code") %>%
  select(Code, `Course Title`, Cluster, n_ILO, n_assessment, `Assessments Covered`, n_AoD, `AoD Covered`, everything())
print(d_course)
```

The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level). Yet, these course are also offered at the `2000` level (intermediate level). We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
```{r}
d_course <- d_course %>%
  rbind(filter(., Code %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
          mutate(Code = case_when(Code == "UGR3001" ~ "UGR2001",
                                  Code == "UGR3002" ~ "UGR2002",
                                  Code == "UGR3003" ~ "UGR2003",
                                  Code == "UGR3005" ~ "UGR2005")))

@@

Finally, we add a series of informative variable at the course level.
```{r}
d_course <- d_course %>%
  mutate(
    `Missing from ILO File` = as.logical(`Missing from ILO File`),
    Letters = substring(Code, 1, 3),
    Number  = as.numeric(substring(Code, 4, 7)),
    Level   = case_when(between(Number, 1000, 1999) ~ "Introductory",
                        between(Number, 2000, 2999) ~ "Intermediate",
                        between(Number, 3000, 3999) ~ "Advanced"    ))
print(select(d_course, Code, Letters, Number, Level))
```

>>>>

### Courses
Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. The tibble `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains; `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers; `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. We use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
d_ILO_detail <- d_ILO %>% 
  select(Code, ILO) %>%
  distinct() %>%
  count(Code) %>%
  rename(n_ILO = n)

d_assessment_detail <- d_assessment %>%
  group_by(Code) %>%
  summarise(n_assessment = n(),
            `Assessments Covered` = paste(Assessment, collapse = ", "))

d_AoD_detail <- d_AoD %>%
  group_by(Code) %>%
  summarise(n_AoD = n(),
            `AoD Covered` = paste(AoD, collapse = ", "))

d_course_detail <- d_ILO_detail %>%
  full_join(d_assessment_detail, by = "Code") %>%
  full_join(d_AoD_detail       , by = "Code")

rm(d_ILO_detail, d_assessment_detail, d_AoD_detail)
print(d_course_detail)
```

```{r join d_course_detail}
d_course <- full_join(d_course, d_course_detail, by = "Code") %>%
  select(Code, `Course Title`, Cluster, n_ILO, n_assessment, `Assessments Covered`, n_AoD, `AoD Covered`, everything())

rm(d_course_detail)
print(d_course)
```

The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level). Yet, these course are also offered at the `2000` level (intermediate level). We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
```{r create UGR2000}
d_course <- d_course %>%
  rbind(filter(., Code %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
          mutate(Code = case_when(Code == "UGR3001" ~ "UGR2001",
                                  Code == "UGR3002" ~ "UGR2002",
                                  Code == "UGR3003" ~ "UGR2003",
                                  Code == "UGR3005" ~ "UGR2005")))

@@

Finally, we add a series of informative variable at the course level.
```{r d_course additional info}
d_course <- d_course %>%
  mutate(
    `Missing from ILO File` = as.logical(`Missing from ILO File`),
    Letters = substring(Code, 1, 3),
    Number  = as.numeric(substring(Code, 4, 7)),
    Level   = case_when(between(Number, 1000, 1999) ~ "Introductory",
                        between(Number, 2000, 2999) ~ "Intermediate",
                        between(Number, 3000, 3999) ~ "Advanced"    ))
print(select(d_course, Code, Letters, Number, Level))
```
